Titeln på avhandlingens språk

### 2023-03-28 body/part1/chapter1-introduction/background.tex
fixes

\glsreset{MEC}%
In later years, an extension to Edge Computing denoted \gls{MEC} has emerged, which pairs Edge Computing with novel mobile networking standards such as 5G~\cite{hassan2019edge,pham2020survey,wan2020efficient}.
A modern mobile network is composed of two main components: the \gls{RAN} and the core network.
The former includes the base stations and other wireless communication equipment to which user's equipment (i.e.\ mobile phones, mobile internet dongles, etc.) connect. 
The \gls{RAN} provides access to the core network, which in turn routes data between \glspl{RAN}, handles billing and authentication, and provides access to external services such as the internet and the Cloud.
\gls{MEC} is defined as an Edge Computing deployment in which Cloud-like compute is deployed within the \gls{RAN} of a mobile network.
Compute power is never more than a single wireless hop away from users application traffic thus never enters the core or the public internet.
This architectural design has the potential to enable unprecedented use-cases requiring stringent, sub-\SI{10}{\milli\second} latency bounds and high bandwidths.
Two examples of such applications, of relevance for the present work, are \acl{WCA}~\cite{ha2014towards,chen2018application,wang2020scaling,chen2017empirical,chen2018application} and \aclp{NCS}~\cite{sasaki2016vehicle,wang2018bandwidth,wan2020efficient}.
These applications had been hitherto inviable to implement due to the limitations of Cloud offloading in mobile and wearable contexts, but have now become a practical reality thanks to \gls{MEC}.

Finally, another variant of Edge Computing called \emph{fog} computing, introduced by \citeauthor{bonomi2012fog}~\cite{bonomi2012fog} in\ \citeyear{bonomi2012fog}, concerns itself specifically with the distribution of computing power between the Cloud and the edge for the reduction of bandwidth requirements.
By aggregating, transforming, and filtering data at multiple levels in the network, fog computing aims to reduce the load placed on Cloud datacenters by massive \gls{IOT} sensor networks~\cite{yi2015survey}.
Edge Computing also presents opportunities for increased data security, privacy, and integrity, by keeping it geographically close to its origin and by allowing for anonymization through denaturing and local aggregation before offloading to Cloud services~\cite{satyanarayanan2017emergence}.

>>>>

\glsreset{MEC}%
\glsreset{RAN}%
In later years, an extension to Edge Computing denoted \gls{MEC} has emerged, which pairs Edge Computing with novel mobile networking standards such as 5G~\cite{hassan2019edge,pham2020survey,wan2020efficient}.
A modern mobile network is composed of two main components: the \gls{RAN} and the core network.
The former includes the base stations and other wireless communication equipment to which user's equipment (i.e.\ mobile phones, mobile internet dongles, etc.) connect. 
The \gls{RAN} provides access to the core network, which in turn routes data between \glspl{RAN}, handles billing and authentication, and provides access to external services such as the internet and the Cloud.
\gls{MEC} is defined as an Edge Computing deployment in which Cloud-like compute is deployed within the \gls{RAN} of a mobile network.
Compute power is never more than a single wireless hop away from users application traffic thus never enters the core or the public internet.
This architectural design has the potential to enable unprecedented use-cases requiring stringent, sub-\SI{10}{\milli\second} latency bounds and high bandwidths.
Two examples of such applications, of relevance for the present work, are \acl{WCA}~\cite{ha2014towards,chen2018application,wang2020scaling,chen2017empirical,chen2018application} and \aclp{NCS}~\cite{sasaki2016vehicle,wang2018bandwidth,wan2020efficient}.
These applications had been hitherto inviable to implement due to the limitations of Cloud offloading in mobile and wearable contexts, but have now become a practical reality thanks to \gls{MEC}.

Finally, another variant of Edge Computing called \emph{Fog} computing, introduced by \citeauthor{bonomi2012fog}~\cite{bonomi2012fog} in\ \citeyear{bonomi2012fog}, concerns itself specifically with the distribution of computing power between the Cloud and the edge for the reduction of bandwidth requirements.
By aggregating, transforming, and filtering data at multiple levels in the network, Fog computing aims to reduce the load placed on Cloud datacenters by massive \gls{IOT} sensor networks~\cite{yi2015survey}.
Edge Computing also presents opportunities for increased data security, privacy, and integrity, by keeping it geographically close to its origin and by allowing for anonymization through denaturing and local aggregation before offloading to Cloud services~\cite{satyanarayanan2017emergence}.
